CudeleFS: Programmable Consistency and Durability\\in a Global Namespace

### 2017-04-01 paper/sections/3_posix_overheads.tex

@@

>>>>

\begin{figure}[tb]
\centering
\includegraphics[width=1\linewidth]{./graphs/overhead-creates.png}
\caption{Create-heavy workloads (untar) incurr the highest disk, network, and
CPU utilization because of the consistency and durability demands of
CephFS.}\label{fig:overhead-creates}
\end{figure}

@@

% - sequential IO, trim redundant operations
\noindent\textbf{CephFS Design}: a journal of metadata updates that streams into
the resilient object store. Similar to LFS~\cite{rosenblum:acm1992-LFS} and
WAFL~\cite{hitz:wtec1994-WAFL} the metadata journal is designed to grow to large which
ensures (1) sequential writes into the object store and (2) the ability for daemons to
trim redundant or irrelevent journal entries.  The journal is striped over
objects where multiple journal updates can reside on the same object. There are
two tunables for controlling the journal: the segment size and the number of
parallel segments that can be written in parallel. Unless the journal saturates 
memory or CPU resources, larger values for these tunables results in better
performance.

% purpose of the journal
As shown in Figure~\ref{fig:journal}, in addition to the metadata journal,
CephFS also represents metadata in RADOS as a metadata store, where directories
and their file inodes are stored as objects.  The metadata server applies the
updates in the journal to the metadata store when the journal reaches a certain
size. The metadata store is optimized for recovery ({\it i.e.} reading) while
the metadata journal is write-optimized.
